Chemistry of fossil Pinus pollen and the effect of acetolysis

### 2021-03-18 manuscript.Rmd
changed count grain function to check pollen species counts; experimenting on spls with caret pkg

<!-- PCA -->
```{r}
DAL$Label = "DAL"
TSK$Label = "TSK"
MFM$Label = "MFM"

pca_data = rbind(subset(DAL, species == "Pinus"), 
        subset(TSK, species == "Pinus"), 
        subset(MFM, species == "Pinus"))
pca_data[pca_data$treatment == "","treatment"] = "SPT"
pca_res = princomp(pca_data$sg2, scores = T)
scores =  as.data.frame(pca_res$scores[,1:10]) %>%
  mutate(ids = rownames(.), 
         core = pca_data$Label, 
         treatment = pca_data$treatment
         ) #%>%
  #melt(.,id.vars = "ids")
ggplot(scores, aes(Comp.1, Comp.2, color = core)) + geom_point()
# pca_data[scores[scores[,2] < -.2,"ids"]==pca_data$ids,1:10]
```

```{r DALcounts, echo=FALSE, results='asis'}
count_grains = function(core){
  counts = core %>%
    subset(type == "pollen" & species == "Pinus") %>% 
    group_by(type, depth, treatment) %>%
    summarise(count=n())
  return(counts)
}
kable(count_grains(DAL), booktabs = T, format = "latex",
      caption = "Pinus pollen grain count in Dalmutladdo core.")
#      digits = 1, format.args = list(scientific = F),
#      col.names = c("")) %>% 
#  add_header_above()
```

>>>>

<!-- PCA -->
```{r}
DAL$Label = "DAL"
TSK$Label = "TSK"
MFM$Label = "MFM"
```

```{r DALcounts, echo=FALSE, results='asis'}
count_grains = function(core){
  counts = core %>%
    subset(type == "pollen" & species == "Pinus") %>% 
    group_by(type, depth, treatment) %>%
    summarise(count=n())
  return(counts)
}
count_grains = function(core){
  counts = core %>%
    subset(type == "pollen") %>% 
    group_by(treatment, depth, species) %>%
    summarise(count=n())
  return(counts)
}
kable(count_grains(DAL), booktabs = T, format = "latex",
      caption = "Pinus pollen grain count in Dalmutladdo core.")
#      digits = 1, format.args = list(scientific = F),
#      col.names = c("")) %>% 
#  add_header_above()
```
